### 2017-04-10 main.tex
:mortar_board: :beers: :sparkles: :wine_glass: :boom:
Eliminate type 3 fonts from techreport

\newcommand{\sep}[0]{\; | \;}
\newcommand{\kvd}[1]{\textnormal{\textcolor{kvdclr}{\ttfamily #1}}}
\newcommand{\num}[1]{\textcolor{numclr}{#1}}
\newcommand{\str}[1]{\textnormal{\textcolor{strclr}{\sffamily "#1"}}}
\newcommand{\strf}[1]{\textnormal{\textcolor{strclr}{\sffamily #1}}}
\newcommand{\prepk}[1]{\textnormal{\textcolor{prepclr}{\sffamily #1}}}
\newcommand{\prepi}[1]{\textnormal{\textcolor{prepclr}{\ttfamily #1}}}
\newcommand{\ident}[1]{\textnormal{\sffamily #1}}
\newcommand{\cmt}[1]{\textit{\sffamily\textcolor{cmtclr}{#1}}}

@@

\newcommand{\czero}{ \textcolor{cclr}{ \mathsf{ign} } }
\newcommand{\cunit}{ \textcolor{cclr}{ \mathsf{use} } }
\newcommand{\cseq}{ \textcolor{cclr}{ \circledast }}
\newcommand{\cpar}{ \textcolor{cclr}{\oplus} }
\newcommand{\czip}{ \textcolor{cclr}{\wedge} } % only used by flat coeffects
\newcommand{\cleq}{ \textcolor{cclr}{\leq} }
\newcommand{\cgeq}{ \textcolor{cclr}{\geq} }

@@

\newcommand{\sem}[1]{\llbracket #1 \rrbracket}
\newcommand{\catc}{\mathcal{C}}
\newcommand{\idf}[1]{ {\textnormal{\sffamily id}}_{#1} }

\urlstyle{sf}

@@

\begin{document}

@@

\pagenumbering{roman} % Roman page numbering prior to the start of the thesis content (i, ii, iii, etc)

@@

\include{text/Titlepage} % Main title page

\cleardoublepage\include{text/Declaration} % Publications from the thesis page

@@

@@

\pagenumbering{arabic} % Arabic page numbering for thesis content (1, 2, 3, etc)
%\setcounter{page}{90} % Uncomment to manually start the page counter at an arbitrary value (for example if you wish to count the pre-content pages in the page count)

>>>>

\newcommand{\sep}[0]{\; | \;}
\newcommand{\kvd}[1]{\textnormal{\textcolor{kvdclr}{\ttfamily #1}}}
\newcommand{\num}[1]{\textcolor{numclr}{#1}}
\newcommand{\str}[1]{\textnormal{\textcolor{strclr}{\ttfamily "#1"}}}
\newcommand{\strf}[1]{\textnormal{\textcolor{strclr}{\ttfamily #1}}}
\newcommand{\prepk}[1]{\textnormal{\textcolor{prepclr}{\ttfamily #1}}}
\newcommand{\prepi}[1]{\textnormal{\textcolor{prepclr}{\ttfamily #1}}}
\newcommand{\ident}[1]{\textnormal{\ttfamily #1}}
\newcommand{\cmt}[1]{\textit{\ttfamily\textcolor{cmtclr}{#1}}}

@@

\newcommand{\czero}{ \textcolor{cclr}{ \mathtt{ign} } }
\newcommand{\cunit}{ \textcolor{cclr}{ \mathtt{use} } }
\newcommand{\cseq}{ \textcolor{cclr}{ \circledast }}
\newcommand{\cpar}{ \textcolor{cclr}{\oplus} }
\newcommand{\czip}{ \textcolor{cclr}{\wedge} } % only used by flat coeffects
\newcommand{\cleq}{ \textcolor{cclr}{\leq} }
\newcommand{\cgeq}{ \textcolor{cclr}{\geq} }

@@

\newcommand{\sem}[1]{\llbracket #1 \rrbracket}
\newcommand{\catc}{\mathcal{C}}
\newcommand{\idf}[1]{ {\textnormal{\ttfamily id}}_{#1} }

\urlstyle{tt}

@@

\begin{document}
\setcounter{page}{3}

@@

%\pagenumbering{roman} % Roman page numbering prior to the start of the thesis content (i, ii, iii, etc)

@@

%\include{text/Titlepage} % Main title page

%\cleardoublepage\include{text/Declaration} % Publications from the thesis page

@@

\cleardoublepage\include{text/Acknowledgements} % Publications from the thesis page

@@

%\pagenumbering{arabic} % Arabic page numbering for thesis content (1, 2, 3, etc)
%\setcounter{page}{90} % Uncomment to manually start the page counter at an arbitrary value (for example if you wish to count the pre-content pages in the page count)
